Bird beak's elaboration and innovation

### 2022-10-07 Analysis/03.1-Elaboration_innovation_analysis[statistics].Rmd
Update figure EI comparison

```{r, eval = TRUE, echo = FALSE, fig.height = 20, fig.width = 8}
#TODO: make the groups nested in the fable

pdf("../Manuscript/Figures/orthogonality_results.pdf", width = 9, height = 9)
source("../Functions/ploting.utilities.R")
## Plot the orthogonality into context
orthogonality <- all_results[, c(1:2, 9:14, 3, 5)]

@@

legend("topleft", legend = c("Sub-orders (vs. passeriformes)", "Families (vs. sub-orders)", "Families (vs. passeriformes)"), col = c(gg.color.hue(4)[2], gg.color.hue(4)[3], adjustcolor(gg.color.hue(4)[4], alpha.f = 2/3)), pch = c(19, 19, 21), lty = c(1,1,2), cex = 0.8)

@@

@@

pdf("../Manuscript/Figures/relative_EI.pdf", height = 8, width = 8)
par(mfrow = c(2,2))
plot.density(species = c(elaboration_species),
             group   = c(unlist(elaboration_super_orders), unlist(elaboration_orders)),
             xlab    = "relative elaboration", scale.x = TRUE,
             ylab    = "density",
             main    = "A - Total posterior elaboration per group\n(scaled) and per species")
legend("topright", lty = 1, legend = c("species", "groups"), col = c("blue", "orange"))
plot.density(species = c(innovation_species),
             group   = c(unlist(innovation_super_orders), unlist(innovation_orders)),
             xlab    = "relative innovation", scale.x = TRUE,
             ylab    = "density",
             main    = "B - Total posterior innovation per group\n(scaled) and per species")
plot.density(elaboration_species_auc, elaboration_group_auc, scale.x = FALSE, col = c("blue", "orange"), ylab = "density",
             xlab = "Posterior area under the curve (elaboration)",
             main = paste0("C - Difference in amounts of elaboration\nper group or per species\nBhattacharyya coefficient = ",
                           round(bhatt.coeff(elaboration_species_auc, elaboration_group_auc), 3)))
plot.density(innovation_species_auc, innovation_group_auc, scale.x = FALSE, col = c("blue", "orange"), ylab = "density",
             xlab = "Posterior area under the curve (innovation)",
             main = paste0("D - Difference in amounts of innovation\nper group or per species\nBhattacharyya coefficient = ",
                           bhatt.coeff(innovation_species_auc, innovation_group_auc)))
dev.off()
```

>>>>

```{r, eval = TRUE, echo = FALSE, fig.height = 20, fig.width = 8}
#TODO: make the groups nested in the fable
pdf("../Manuscript/Figures/orthogonality_results.pdf", width = 9, height = 9)
source("../Functions/ploting.utilities.R")
## Plot the orthogonality into context
orthogonality <- all_results[, c(1:2, 9:14, 3, 5)]

@@

legend("topleft", legend = c("Sub-orders (vs. passeriformes)", "Families (vs. sub-orders)", "Families (vs. passeriformes)"), col = c(gg.color.hue(4)[3], gg.color.hue(4)[4], adjustcolor(gg.color.hue(4)[4], alpha.f = 2/3)), pch = c(19, 19, 21), lty = c(1,1,2), cex = 0.8)

@@

## Testing whether clades innovate more than species

@@

pdf("../Manuscript/Figures/relative_EI.pdf", height = 6, width = 12)
par(mfrow = c(1,2))
plot.density(species = c(elaboration_species),
             group   = c(unlist(elaboration_super_orders), unlist(elaboration_orders)),
             xlab    = "relative elaboration", scale.x = TRUE,
             ylab    = "density",
             main    = "A - Total posterior elaboration per clade\n(scaled) and per species")
legend("topright", lty = 1, legend = c("species", "clades"), col = c("blue", "orange"))
text(x = 0.7, y = 0.5, paste0("Posterior area under the curve overlap\n(Bhattacharyya coefficient): ", round(bhatt.coeff(elaboration_species_auc, elaboration_group_auc), 3)))
plot.density(species = c(innovation_species),
             group   = c(unlist(innovation_super_orders), unlist(innovation_orders)),
             xlab    = "relative innovation", scale.x = TRUE,
             ylab    = "density",
             main    = "B - Total posterior innovation per clade\n(scaled) and per species")
text(x = 0.7, y = 0.5, paste0("Posterior area under the curve overlap\n(Bhattacharyya coefficient): ", round(bhatt.coeff(innovation_species_auc, innovation_group_auc), 3)))
dev.off()
```
